\section{Resources}
\label{chap:Resources}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  % SUBSECTION               %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Google Colaboratory}
Colab. is a Google research project created to help disseminate machine learning education and research. It's a Jupyter notebook environment that requires no setup to use and runs entirely in the cloud free GPU in one VM for 12 hours. Colab notebooks are stored in Google Drive and can be shared just as you would with Google Docs or Sheets. Colab supports both Python2 and Python3 for code execution and its libraries with easy installation using (!pip install requests). Colab is free to use. Colab also supports connecting to a Jupyter runtime on your local machine.Colab provides Tesla K80 GPU and 13 Giga RAM.\\FOR USAGE, VISIT: https://colab.research.google.com/notebooks/welcome.ipynb
\subsection{Valohai}
Valohai is end-to-end machine learning tool which provides an interface for powerful amazon instances with cuda enabled GPUs such as Tesla v100 and Telsa k80 such as P3 and M4 amazon instances.
We emailed them and asked for credit as they announced for free support for open source projects and research.\\
FOR USAGE, VISIT: https://valohai.com
\subsection{Intel® AI DevCloud}
Intel AI DevCloud, a cloud hosted hardware and software platform available to developers, researchers and startups to learn, sandbox and get started on their AI  projects. Intel® Academy members can gain free access to the DevCloud powered by Intel® Xeon® Scalable Processors for their machine learning and deep learning compute needs. \\
When you gain access to the DevCloud, you will log into a Linux-based head node of a batch farm. There you can stage your code and data, compile, and submit jobs to a queue. Once the queued job completes, your results will be in your home folder. Features:\\
\indent$\bullet$Jobs are scheduled on Intel® Xeon® Scalable Processors.\\
\indent$\bullet$Each processor has 24 cores with 2-way hyper-threading.\\
\indent$\bullet$Each processor has access to 96 GB of on-platform RAM (DDR4).\\
\indent$\bullet$Only one job will run on any processor at a time.\\
\indent$\bullet$You will get 200 GB of file storage quota.\\
\indent$\bullet$Your home directory is not visible to other users.\\
\indent$\bullet$Once your access period expires, your home directory on the cluster will be deleted.\\
FOR USAGE, VISIT: https://ai.intel.com/devcloud

